Token-level author diarization using clustering of stylistic contexts

### 2017-06-02 paper/paper.tex
no message

\citet{zu-2006} manually created a labelled corpus of plagiarized documents and used it for intrinsic plagiarism detection task. They used average sentence length, part of speech tags, average stop word number and the averaged word frequency class as input features for their linear discriminant analysis and support vector machine (SVM) models. They approached that task in a supervised fashion.

@@

\subsection{Experimental setup}
In every task we used the same tokenization procedure as described in section \ref{sec:the-proposed-approach}. Model A covers all three tasks and has several hyperparameters for each of them: context size, clustering algorithm and its hyperparameters.

\paragraph{Model A.}Context size was determined manually for tasks \emph{a} and \emph{b}, in a similar way as feature selection. We used a whole dataset and default implementation of k-means from \texttt{scikit-learn} and tested different values. The best result for task \emph{a} was $cs_a=16$ and for task \emph{b} $cs_b=140$. For task \emph{c}, we left $cs_c=140$ as for task \emph{b}. This hyperparameter probably depends on document's length to a certain extent. If we compare that sizes with the average document lengths in tokens across datasets, we can see that there is a correspondence ($1679, 3767, 3298$ vs. $16, 140, 140$). However, they are probably biased to a certain extent.

>>>>

\citet{zu-2006} have manually created a labelled corpus of plagiarized documents and used it for the intrinsic plagiarism detection task. They used average sentence length, part of speech tags, average stop word number and the averaged word frequency class as input features for their linear discriminant analysis and support vector machine (SVM) models. They approached that task in a supervised fashion.

@@

\subsection{Experimental setup}
In every task we used the same tokenization procedure as described in section \ref{sec:the-proposed-approach}. Model A covers all three tasks and has several hyperparameters for each of them: context size, clustering algorithm and its hyperparameters. Model B uses a smaller set of features and trainable feature transformations with most of the hyperparameters equal among the tasks.

\paragraph{Model A.} Context size was determined manually for tasks \emph{a} and \emph{b}, in a similar way as feature selection. We used a whole dataset and default implementation of k-means from \texttt{scikit-learn} and tested different values. The best result for task \emph{a} was $cs_a=16$ and for task \emph{b} $cs_b=140$. For task \emph{c}, we left $cs_c=140$ as for task \emph{b}. This hyperparameter probably depends on document's length to a certain extent. If we compare that sizes with the average document lengths in tokens across datasets, we can see that there is a correspondence ($1679, 3767, 3298$ vs. $16, 140, 140$). However, they are probably biased to a certain extent.
